Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-18 cordillera-cycle.tex
Add section 4.1.3.

\todo{Add MIS~4 ice topo and velocity map. Discuss that some of the margins
      are more extensive during MIS~4 than during MIS~2 in the GRIP simulation}

(Fig.~\ref{fig:snapshots}, upper panels; Fig.~\ref{fig:mis4})
(Fig.~\ref{fig:mis4})

>>>>

The modelled ice sheet configurations corresponding to ice volume maxima during
MIS~4 are more variable (Fig.~\ref{fig:snapshots}, upper panels;
Fig.~\ref{fig:mis4}). The GRIP simulation (Fig.~\ref{fig:mis4}, left panel)
results in a modelled maximum ice sheet that closely resemble that obtained
during MIS~2, with the only major differences being a slightly less developed
northern and eastern sectors. However, the EPICA simulations produce a reduced
ice volume maximum (Fig.~\ref{fig:timeseries}), which translates in the
modelled ice sheet geometry into a much less developed southern sector, more
restricted ice cover on the northern and eastern flanks, and generally lower
ice surface elevations in the interior (Fig.~\ref{fig:mis4}, left panel).

In the GRIP simulation, some sections of the MIS~4 maximum ice margin are
slightly more extensive than their MIS~2 counterparts. This is notably the case
in the Puget Lowland, along parts of the marine margin, and parts of the north
slope of the Alaska Range. However, these differences generally correspond to a
few model grid cells. Their interpretation would be hazardous considering
the simplicity of our atmospheric forcing, and the scale of our simulations.
